JARINGAN DAN PENGOLAHAN DATA PARALEL

### 2021-12-31 Semester I/Jaringan dan Pengolahan Data Paralel/praktikum/Laporan Praktikum.Rmd
new

metode = c("Serial","Serial",
	   "Broadcast","Broadcast",
	   "Broadcast Gather","Broadcast Gather",
	   "Broadcast Reduce","Broadcast Reduce",
	   "Gather","Gather",
	   "Multi Processing","Multi Threading","P2P",
	   "Reduce","Scatter","Scatter Gather","Scatter Reduce")

@@

nilai = c(3.1415926535908407,3.141628338857705,
	  3.1415926535908407,3.141587559754934,
	  3.141592653590117,25.132540181445272/8,
	  3.1415926535901164,25.13158041365358/8,
	  3.141592653590117,25.131631135260793/8)
runtime = c(37.09915375709534,34.31454539299011,
	    80.7673327922821,72.39736461639404,
	    10.181049823760986,9.693099021911621,
	    10.260845422744751,9.936588048934937,
	    10.22980284690857,9.260202646255493)

>>>>

metode = c("Serial","Serial",
	   "Broadcast","Broadcast",
	   "Broadcast Gather","Broadcast Gather",
	   "Broadcast Reduce","Broadcast Reduce",
	   "Gather","Gather",
	   "Multi Processing","Multi Processing",
	   "Multi Threading","Multi Threading",
	   "P2P","P2P",
	   "Reduce","Reduce",
	   "Scatter","Scatter Gather","Scatter Reduce")

@@

nilai = c(3.1415926535908407,3.141628338857705,
	  3.1415926535908407,3.141587559754934,
	  3.141592653590117,25.132540181445272/8,
	  3.1415926535901164,25.13158041365358/8,
	  3.141592653590117,25.131631135260793/8,
	  3.1415926535901084,3.141520140116895,
	  3.1415926535908407,3.1414638257166785,
	  3.149869484774846845,3.1414060525250656,
	  3.1415926535901164,25.130795204732536/8,
	  )
runtime = c(37.09915375709534,34.31454539299011,
	    80.7673327922821,72.39736461639404,
	    10.181049823760986,9.693099021911621,
	    10.260845422744751,9.936588048934937,
	    10.22980284690857,9.260202646255493,
	    10.83942699432373,9.118600368499756,
	    40.60416913032532,33.76176381111145,
	    10.335948376,9.111383716,
	    10.357647895812988,9.344260215759277,
	    )
